---
title: "Zhen STAT 450 Assignment1"
author: "Zhen Liu"
date: "2018/1/11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction about Myself

I am Zhen Liu. I came from China. I came to Canada in 2015. I am majoring in Statistics and minoring in Commerce. I am in my final year of my Bachelor's studies. STAT 450 is a challenging course for me. I hope I can learn more skills to solve practical problems about Statistics from this course. This is my first time using R markdown. 

## My Favourite Equation
Population mean = $\mu$ = $\frac{\sum_{i=1}^{N}X_i}{N}$, where N is the pupulation size. This is my favourite equation beacuse $\textbf{mean}$ is the most common statistic used to measure the center of a numerical data set. Also, $\textbf{population mean}$ is the mean of the entire population.

## Discussion for Dataset
My favoriate city is my hometown, Changsha. I did not stay in Changsha last year so I am very curious about the temperature change of my hometown last year.
```{r}
MyDataset = data.frame(Month = c(1:12), Temperature =c(-1,5,10,14,25,30,35,36,30,28,12,2))
head(MyDataset,5)  #first five rows of my dataset
```


## Scatter plot of MyDataset
The following is the scatter plot of my dataset.

```{r plot, echo=FALSE}
plot(MyDataset$Month,MyDataset$Temprature, main = 'Monthly Average Temperature of Changsha in 2017', xlab = 'Month',ylab = 'Temperature(C)')
```
